\Paragraph{Secure that should be secure}
%
The security problem is one of the most critical for a variety of software. 
%
User trusts such software to perform operations most important from security point of view, for example, processing of his personal data \Reference{Winograd2008}. 
%
Examples of software that should be secure are following: servers available from network, web applications, applets, daemons, as well as applications that have appropriate access rights to perform a privileged operation. 

\Paragraph{The concept of secure software}
%
To be considered as a secure software it should be designed, implemented, configured, and maintained in such a way as to operate properly under attack by a malicious person and to reduce effects of software defects that are independent from the software \Reference{Goertzel2007}. 
%
Secure software has the following properties: reliability, trustworthiness, and reducibility \Reference{Winograd2008}. 
%
Reliable software operates properly under any circumstances, including attacks. 
%
Software that has trustworthiness property does not contain operations that could be used to injury the software by a malicious person. 
%
Software that has reduciblity property is tolerant to attacks and can recover it's proper operating after their performing. 

\Paragraph{The concept of software security assurance}
%
As much developer takes into consideration these factors as more secure software is developed by him. 
%
It allows him to engage security assurance activities related to the software. 
%
According \Reference{Goertzel2007}, software security assurance consists of ``a planned and systematic set of activities that are intended for meeting by the software security requirements, standards and procedures''. 
%
McGraw gives three pillars of software security: risk management, developer's knowledge about software security, and compliance with practices specific to security \Reference{McGraw2006}.
%
Software security assurance is based on these pillars. 

\Paragraph{Transition to software security analysis}
%
As it was noted in \InReferenceToSection{introduction_main_objectives}, the practical part of the thesis is comprised of search of software vulnerabilities. 
%
It is explained by the fact that the project being investigated is on a testing stage of it's development lifecycle. 
%
Search of software vulnerabilites is performed by means of it's security analysis. 