\Paragraph{Concept}
%
As it was noted above, availablity of source code is required to perform white box testing. 
%
Applying of methods that utilize source code are most useful and popular at development stage. 
%
These methods involve static and dynamic source code analysis, and property-based testing \Reference{Winograd2008}. 

\Paragraph{Advantages and disadvantages}
%
White box testing has a number of advantages and disadvantages \Reference{Sutton2007}. 
%
The main advantage is \A high degree of source code coverage owing it's availability. 
%
All possible application executing paths are analyzed to find potential security vulnerabilities. 
%
Whereas the main disadvantage is complexity of performing this kind of analysis itself. 
%
It is not rare when an analyzer gives a lot of false results, especially if testing software is sizeable. 

% -------------------------------------------------------------------------------------------------

\SubSubSectionTitle{Source code static analysis}
	{software_security_analysis_blackbox_testing_techniques_static_code_analysis}

\Paragraph{The main disadvantage of secure programming technique}
%
The secure programming technique \Reference{McConnell2004} is utilized to defense against invalid input data on all implemented software levels. 
%
It promotes faster detection of errors and rise of software security integrally. 
%
But application of the analysis is not enough \Reference{Chess2007}. 
%
It is directed to check whether calling party complies with the contract of appropriate called party. 
%
Transfering data safety is not assured. 

\Paragraph{Example of the problem}
%
In the listing below, a function of message logging is presented. 
%
Specially formed value of \SourceCode{msg} argument can be valid but it is leading to the vulnerability of \SourceCode{fprintf()} format function in the body of this function. 
% !!! TODO: (see \ReferenceToSection{software_security_vulnerabilities_format_strings}). 
%
Such kind of vulnerabilities can be found by means of performing static analysis. 

\Listing{Unsafe program example}{C}
	{listings/software_security_analysis/static_analysis.c}

\Paragraph{The concept}
%
Static analysis carrying out leads to search of various problems such as errors committed by accident, common programming errors, including security vulnerabilities \Reference{Chess2007}. 
%
Source code static analysis helps to reduce \A total number of such kind of errors as early as at development stage. 

\Paragraph{Static analysis and source code revision}
%
Static analysis is often performed during the process of source code revision. 
%
In this case the revision is performed sequentially. 
It involves the following steps \Reference{Chess2007}: 
\begin{itemize}
	\item goals of revision are established
	\item static analysis tools are utilized
	\item then accoring to the reports of their work source code revision is performed itself
	\item found errors are eliminated
\end{itemize}

\Paragraph{Static analysis disadvantages}
%
Static analysis carrying out has a number of disadvantages \Reference{Winograd2008} \Reference{Chess2007}. 
%
It can be used only as an additional tool in the process of error detection. 
%
It can be explained by the fact that error absence in the report does not mean that they do not exist in a tested application. 
%
For example, errors invisible in the code explicitly but become apparent during the application execution are referred to such kind of errors. 
%
Also, a static analysis tool report often contains a lot of false positives. 
%
Threrefore the analysis should be performed by a security high-skilled expert. 

\Paragraph{Well-known static analysis tools}
%
The well-known static analysis tools are the following: \IT{Splint} \WebSite{Splint}, \IT{Cppcheck} \WebSite{Cppcheck}, \IT{RATS} \WebSite{RATS}, \IT{ITS4} \WebSite{ITS4}, \IT{PVS Studio} \WebSite{PVSStudio}, and others.
%
\IT{RATS} and \IT{PVS Studio} can be used to search concurrency problems, including race conditions. 
%
\IT{ITS4} and \IT{Splint} are intended to search of known vulnerabilities specific to \IT{C} and \IT{C++} programming languages, for example, buffer overflow, format function vulnerabilities, and others. 
% !!! TODO: (see \ReferenceToSection{software_security_vulnerabilities_format_strings}). 

% -------------------------------------------------------------------------------------------------

\SubSubSectionTitle{Property-based testing}
	{software_security_analysis_blackbox_testing_techniques_property_based_testing}

\Paragraph{Description}
%
Purpose of any set of software tests is to examine reliability and functionality of tested software. 
%
In other words, verification of software semantic characteristics is carried out. 
%
This kind of testing is a variety of formal analysis techniques, threrefore it is utilized only after implementation of declared tested software features \Reference{Winograd2008}. 

\Paragraph{How is it performed}
%
To perform property-based testing the following steps are carried out \Reference{Fink1997}. 
%
Specification of tested software is analyzed. 
%
On the basis of the specification, a list of the tested software properties is formed. 
%
These properties, for instance, correctness of authentication mechanism, should be verified. 
%
Then verification of each property is formalized, \The appropriate test is prepared. 
%
The process of verification is performed using source code. 

\Paragraph{Disadvantages}
%
The main disadvantage of property-based testing is the fact that it requires a lot of time to perform all activities listed above \Reference{Winograd2008}. 
%
Especially, if the tested software is quite sizeable. 
%
The main reason of the disadvantage is \The requirement to prepare strictly formalized tests.