\vspace*{10em}
\italic{Dedicated to the memory of Arkadiy Botyan, my grandfather (1936-2008).}
\newpage
\preamblesectiontitle{Preface}
\nextparagraph{PeerHood}
This project is done as a part of the PeerHood project in Communications Software laboratory of
Lappeenranta University of Technology. I would like to thank for this great opportunity to be
involved of this project and provided guidance for my thesis work.
\nextparagraph{Supervisors}
First and foremost I would like to thank my supervisor, D.Sc. Pekka J\"appinen, for suggested
contemporary and interesting research topic, for his guidance and advice. I am grateful to my second
supervisor, Esa Kerttula, for giving positive and valuable feedback. Without their assistance this
work would not have been possible.
\nextparagraph{Family}
I would like to express my sincere gratitude my parents and brother. They have supported me during
the course of this dissertation.
\nextparagraph{Colleagues, friends, etc.}
Finally, many thanks to Em\={i}ls \u{S}i\cb l\cb nevs, Camilo Andr\'{e}s
Cifuents Genoy, Mihai Iu\c{s}an, Bishal Raj Karki, all the colleagues, and all those helping hands
who directly or indirectly supported, encouraged and helped to accomplish my thesis.
\vspace*{3em}
\par Lappeenranta,\ \thesisdate
\vspace*{3em}
\par Igor Botyan
%
\begin{comment}
INSTRUCTIONS FOR WRITING A MASTER'S THESIS

The contents of this page are totally up to the author. Acknowledgements, mentioning
something about the laboratory/working place/key people furthering the work may be
mentioned. See the “Final thesis instructions” in the study guide.

FINAL THESIS INSTRUCTIONS.

Acknowledgements are a brief description of what or who had an impact on the thesis. 
E.g. the people who furthered the progress of the thesis may be thanked.

===

The acknowledgements recognise the help, guidance, advice etc. provided by others and give
thanks to them. Also the commissioner of the thesis is mentioned. The acknowledgements are
concluded with the author’s name and the date after which no more modifications have been made
to the work.

HOW TO WRITE ACKNOWLEDGMENETS PAGE

What Is Dissertation Acknowledgement?
Dissertation acknowledgment gives you a chance to show your gratefulness for the people who helped 
you with your dissertation writing. 
In Dissertation Acknowledgement you show your appreciation to anybody or any group that may have 
contributed in your dissertation writing directly or indirectly.

How to write dissertation Acknowledgement 
1. Give a heading of dissertation acknowledgement.
2. The heading should be in the center.
3. Then give at lease 4 line space and start your dissertation acknowledgement with the following 
lines or similar

This thesis would not have been possible unless…..
I am grateful……
It is a pleasure to thank those who made this thesis possible…. 
I owe my deepest gratitude to……….

4. Now narrow down the people who you want to thank. They can be your
Supervisor 
Professors 
Advisors 
Colleagues 
Parents 
Friends

Or any other who may have helped you

5. Make sure you mention that it would have been next to impossible to write this thesis without 
help and guidance.

Final Note
Dissertation acknowledgement can have a strategic value. 
Giving some credit to your dissertation advisor is always recommendable as you shift the credit 
to him, increasing the chances of your dissertation getting accepted.
\end{comment}