\begin{titlepage}
\MakeUppercase{\thesisschool}

\vspace*{13em}

{\Large \textbf{\MakeUppercase{\thesistitlewrapped}}}

\vspace*{11em}

\begin{tabbing}
\thesissubject\\
\\
Supervisor:\quad\= \thesissupervisor\\
\\
Examiners:\quad\= \thesisfirstexaminer\\
\> \thesissecondexaminer\\
\\
Lappeenranta,\ \thesisdate
\end{tabbing}

\vspace*{2em}

\thesisauthor\\
Liesharjunkatu 6 D 35\\
53850 Lappeenranta\\
Tel. +358\ 46\ 599\ 0559\\
igor.botyan{@}lut.fi

\end{titlepage}

\begin{comment}
FINAL THESIS INSTRUCTIONS.

The title page includes the title of the thesis. 
The title must be well-defined and correspond to the content of the thesis. 
A keyword, which expresses something essential about the thesis and has an explicit and specific
meaning, is recommended as the first word. 
Avoid the following: some, review, method, report, study, equipment etc.

===

The title page is the first page of the thesis – page number 1. However, the page numbers are not
shown before the first page of the table of contents. The faculty decides on the information
presented on the cover page. However, the following is always printed on it: university, faculty,
degree programme and/or major subject name of author title of thesis examiners (1st and 2nd).

The points above are not to be used as headings on the title page, e.g. University: Lappeenranta
University of Technology is incorrect, but Lappeenranta University of Technology, Faculty of
Technology is correct. The layout of the title page should be balanced, such as in assignment
reports.
\end{comment}